---
title: "contributions"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(here)
library(fuzzyjoin)
library(stringr)
library(ggthemes)
library(ggrepel)
library(extrafont)
library(hrbrthemes)
library(xkcd)
library(cowplot)
library(magick)
library(zoo)
library(gganimate)
library(ggimage)
library(beeswarm)
library(ggbeeswarm)

nhl = read_csv("tulloch.csv") %>% 
  filter(season == "20182019")
```

```{r}
nhl = nhl %>% 
  group_by(Team) %>% 
  mutate(teamG = sum(G),
         A = A1 + A2,
         teamA = sum(A)) %>% 
  mutate(gcont = (G/teamG)*100,
         acont = (A/teamA)*100)

desc_dry = "Draisaitl leads in goal contribution"

nhl %>% 
  ggplot(aes(acont,gcont)) + 
  geom_point(data = nhl %>%
                    filter(gcont < 20 | acont < 15),
             color = "grey20", size = 3, alpha = 0.2) +
  geom_point(data = nhl %>%
                    filter(gcont > 20 | acont > 15),
             color = "red", size = 4) +
  theme_minimal() +
  theme(text = element_text(family = "Roboto Condensed"),
        title = element_text(size = 18),
        plot.subtitle = element_text(size = 16),
        plot.caption = element_text(size = 10),
        axis.title = element_text(size = 14),
        axis.text = element_text(size = 12)) + 
  geom_hline(yintercept = 10, color = "grey20", alpha = 0.4) +
  geom_vline(xintercept = 10, color = "grey20", alpha = 0.4) +
  geom_text_repel(data = nhl %>%
                    filter(gcont > 20 | acont > 15,),
                  aes(label = player, family = "Roboto Condensed", fontface = "bold"), 
                  seed = 15, size = 3, 
                  min.segment.length = 0, segment.color = "red",
                  point.padding = 0.5) +
  labs(title = "Goal Contribution Matrix: NHL (2018-2019 Season)", subtitle = "Team Goal Involvement as Percentage of Total Team Goals/Assists", x="Percentage of Team Goals Assisted", y = "Percentage of Team Goals Scored")

ggsave("contribution.jpg")
```

```{r}
nhl = nhl %>% 
  group_by(Team) %>% 
  mutate(teamG = sum(G),
         A = A1 + A2,
         teamA = sum(A)) %>% 
  mutate(gcont = (G/teamG)*100,
         acont = (A/teamA)*100)

nhl %>% 
  select(player, gcont,acont) %>% 
  arrange(desc(acont))

desc_dry = "Draisaitl leads in goal contribution"

nhl %>% 
  ggplot(aes(acont,gcont)) + 
  geom_point(data = nhl %>%
                    filter(gcont < 20 | acont < 15),
             color = "grey20", size = 3, alpha = 0.2) +
  geom_point(data = nhl %>%
                    filter(gcont > 20 | acont > 15),
             color = "red", size = 4) +
  theme_fivethirtyeight() +
  geom_hline(yintercept = 10, color = "grey20", alpha = 0.4) +
  geom_vline(xintercept = 10, color = "grey20", alpha = 0.4) +
  geom_text_repel(data = nhl %>%
                    filter(gcont > 20 | acont > 15,),
                  aes(label = player, family = "Roboto Condensed", fontface = "bold"), 
                  seed = 15, size = 3, 
                  min.segment.length = 0, segment.color = "red",
                  point.padding = 0.5) +
  labs(title = "Goal Contribution Matrix: NHL (2018-2019 Season)", subtitle = "Team Goal Involvement as Percentage of Total Team Goals/Assists", x="Percentage of Team Goals Assisted", y = "Percentage of Team Goals Scored")

ggsave("contributions2.png")
```

```{r}
```{r}
nhl = nhl %>% 
  group_by(Team) %>% 
  mutate(teamG = sum(G),
         A = A1 + A2,
         teamA = sum(A)) %>% 
  mutate(gcont = (G/teamG)*100,
         acont = (A/teamA)*100)

desc_dry = "Draisaitl leads in goal contribution"

nhl %>% 
  ggplot(aes(acont,gcont)) + 
  geom_point(data = nhl %>%
                    filter(gcont < 20 | acont < 15),
             color = "grey20", size = 3, alpha = 0.2) +
  geom_point(data = nhl %>%
                    filter(gcont > 20 | acont > 15),
             color = "red", size = 4) +
  theme_minimal() +
  theme(text = element_text(family = "Roboto Condensed"),
        title = element_text(size = 18),
        plot.subtitle = element_text(size = 16),
        plot.caption = element_text(size = 10),
        axis.title = element_text(size = 14),
        axis.text = element_text(size = 12)) + 
  geom_hline(yintercept = 10, color = "grey20", alpha = 0.4) +
  geom_vline(xintercept = 10, color = "grey20", alpha = 0.4) +
  geom_text_repel(data = nhl %>%
                    filter(gcont > 20 | acont > 15,),
                  aes(label = player, family = "Roboto Condensed", fontface = "bold"), 
                  seed = 15, size = 3, 
                  min.segment.length = 0, segment.color = "red",
                  point.padding = 0.5) +
  labs(title = "Goal Contribution Matrix: NHL (2018-2019 Season)", subtitle = "Team Goal Involvement as Percentage of Total Team Goals/Assists", x="Percentage of Team Goals Assisted", y = "Percentage of Team Goals Scored")

ggsave("contribution.jpg")
```

```{r}
nhl = nhl %>% 
  group_by(Team) %>% 
  mutate(teamG = sum(G),
         A = A1 + A2,
         teamA = sum(A)) %>% 
  mutate(gcont = (G/teamG)*100,
         acont = (A/teamA)*100)

nhl %>% 
  ggplot(aes(acont,gcont)) + 
  geom_jitter(data = nhl,
             color = "grey20", size = 3, alpha = 0.2) +
  geom_jitter(data = nhl %>%
                    filter(Team == "TOR"),
             color = "#00205B", size = 4, alpha = 0.6) +
  theme_fivethirtyeight() +
  geom_hline(yintercept = 10, color = "grey20", alpha = 0.4) +
  geom_vline(xintercept = 10, color = "grey20", alpha = 0.4) +
  geom_text_repel(data = nhl %>%
                    filter(Team == "TOR" & (gcont>7 | acont>7)),
                  aes(label = player, family = "Roboto Condensed", fontface = "bold"), 
                  seed = 15, size = 3, 
                  min.segment.length = 0, segment.color = "red",
                  point.padding = 0.5) +
  labs(title = "Goal Contribution Matrix: Leafs", subtitle = "Team Goal Involvement as Percentage of Total Team Goals/Assists", x="Percentage of Team Goals Assisted", y = "Percentage of Team Goals Scored")

ggsave("contributions3.png")
```

```{r}
nhl = nhl %>% 
  group_by(Team) %>% 
  mutate(teamG = sum(G),
         A = A1 + A2,
         teamA = sum(A)) %>% 
  mutate(gcont = (G/teamG)*100,
         acont = (A/teamA)*100)

nhl %>% 
  ggplot(aes(acont,gcont)) + 
  geom_jitter(data = nhl,
             color = "grey20", size = 3, alpha = 0.2) +
  geom_jitter(data = nhl %>%
                    filter(Team == "EDM"),
             color = "#FF4C00", size = 4, alpha = 0.6) +
  theme_fivethirtyeight() +
  geom_hline(yintercept = 10, color = "grey20", alpha = 0.4) +
  geom_vline(xintercept = 10, color = "grey20", alpha = 0.4) +
  geom_text_repel(data = nhl %>%
                    filter(Team == "EDM" & (gcont>7 | acont>7)),
                  aes(label = player, family = "Roboto Condensed", fontface = "bold"), 
                  seed = 15, size = 3, 
                  min.segment.length = 0, segment.color = "red",
                  point.padding = 0.5) +
  labs(title = "Goal Contribution Matrix: Oilers", subtitle = "Team Goal Involvement as Percentage of Total Team Goals/Assists", x="Percentage of Team Goals Assisted", y = "Percentage of Team Goals Scored")

ggsave("contributions4.png")
```

```{r}
atlantic = nhl %>% 
  filter(Team == "T.B" | Team =="TOR" | Team == "FLA" | Team == "MTL" | Team == "DET" | Team == "BUF"| Team == "BOS" | Team == "OTT") %>% 
  group_by(Team) %>% 
  mutate(teamG = sum(G),
         A = A1 + A2,
         teamA = sum(A)) %>% 
  mutate(gcont = (G/teamG)*100,
         acont = (A/teamA)*100)

atlantic2 = atlantic %>% 
  mutate(player = gsub("^.*\\.","", player))

atlantic2 %>% 
  ggplot(aes(acont,gcont)) + 
  geom_point(data = atlantic2,
             color = "grey20", size = 2, alpha = 0.2) +
  geom_point(data = atlantic2 %>%
                    filter(Team == "TOR" & (gcont>10 | acont>10)),
             color = "#00205B", size = 2.5, alpha = 0.6) +
  geom_text_repel(data = atlantic2 %>%
                    filter(Team == "TOR" & (gcont>10 | acont>10)),
                  aes(label = player, family = "Roboto Condensed", fontface = "bold"), 
                  seed = 15, size = 1.5, 
                  
                  point.padding = 0.05) +
  geom_point(data = atlantic2 %>%
                    filter(Team == "BOS" & (gcont>10 | acont>10)),
             color = "#FFB81C", size = 2.5, alpha = 0.6) +
  geom_text_repel(data = atlantic2 %>%
                    filter(Team == "BOS" & (gcont>10 | acont>10)),
                  aes(label = player, family = "Roboto Condensed", fontface = "bold"), 
                  seed = 15, size = 1.5, 
                  
                  point.padding = 0.05) +
  geom_point(data = atlantic2 %>%
                    filter(Team == "BUF" & (gcont>10 | acont>10)),
             color = "#002654", size = 2.5, alpha = 0.6) +
  geom_text_repel(data = atlantic2 %>%
                    filter(Team == "BUF" & (gcont>10 | acont>10)),
                  aes(label = player, family = "Roboto Condensed", fontface = "bold"), 
                  seed = 15, size = 1.5, 
                  
                  point.padding = 0.05) +
  geom_point(data = atlantic2 %>%
                    filter(Team == "DET" & (gcont>10 | acont>10)),
             color = "#CE1126", size = 2.5, alpha = 0.6) +
  geom_text_repel(data = atlantic2 %>%
                    filter(Team == "DET" & (gcont>10 | acont>10)),
                  aes(label = player, family = "Roboto Condensed", fontface = "bold"), 
                  seed = 15, size = 1.5, 
                  
                  point.padding = 0.05) +
  geom_point(data = atlantic2 %>%
                    filter(Team == "FLA" & (gcont>10 | acont>10)),
             color = "#B9975B", size = 2.5, alpha = 0.6) +
  geom_text_repel(data = atlantic2 %>%
                    filter(Team == "FLA" & (gcont>10 | acont>10)),
                  aes(label = player, family = "Roboto Condensed", fontface = "bold"), 
                  seed = 15, size = 1.5, 
                  
                  point.padding = 0.05) +
  geom_point(data = atlantic2 %>%
                    filter(Team == "MTL" & (gcont>10 | acont>10)),
             color = "#AF1E2D", size = 2.5, alpha = 0.6) +
  geom_text_repel(data = atlantic2 %>%
                    filter(Team == "MTL" & (gcont>10 | acont>10)),
                  aes(label = player, family = "Roboto Condensed", fontface = "bold"), 
                  seed = 15, size = 1.5, 
                  
                  point.padding = 0.05) +
  geom_point(data = atlantic2 %>%
                    filter(Team == "OTT" & (gcont>10 | acont>10)),
             color = "#C52032", size = 2.5, alpha = 0.6) +
  geom_text_repel(data = atlantic2 %>%
                    filter(Team == "OTT" & (gcont>10 | acont>10)),
                  aes(label = player, family = "Roboto Condensed", fontface = "bold"), 
                  seed = 15, size = 1.5, 
                  
                  point.padding = 0.05) +
  geom_point(data = atlantic2 %>%
                    filter(Team == "T.B" & (gcont>10 | acont>10)),
             color = "#002868", size = 2.5, alpha = 0.6) +
  geom_text_repel(data = atlantic2 %>%
                    filter(Team == "T.B" & (gcont>10 | acont>10)),
                  aes(label = player, family = "Roboto Condensed", fontface = "bold"), 
                  seed = 15, size = 1.5, 
                  
                  point.padding = 0.05) +
  theme_fivethirtyeight() +
  geom_hline(yintercept = 10, color = "grey20", alpha = 0.4) +
  geom_vline(xintercept = 10, color = "grey20", alpha = 0.4) +
  labs(title = "Goal Contribution Matrix: Atlantic", subtitle = "Team Goal Involvement as Percentage of Total Team Goals/Assists", x="Percentage of Team Goals Assisted", y = "Percentage of Team Goals Scored") +
  facet_wrap(~Team) +
  expand_limits(x=20,y=20) +
  theme(axis.text=element_text(size=8)) +
  + theme(axis.title.x = element_text(color="blue", size=14, face="bold"))

ggsave("contributions5.png")
```

